Tropical Mathematics for the Lambda Calculus

### 2023-01-15 section4.tex
commit

To study what happens in the case of tropical Laurent series, let us first consider the case of bounded exponentials $!_{\leq n}X$:
\begin{proposition}\label{prop:boundedlip}
All tropical linear functions $f: \Lawv^{\C M_{\leq n}(X)}\to \Lawv^{Y}$ are $n$-Lipschitz-continuous.
\end{proposition}
\begin{proof}[Proof sketch]
Using the fact that $f(\B x)_{b}=\inf_{\mu\in \C M_{\leq n}(X)}\{ \check f_{\mu,b}+ \mu (!_{n}\B x) \}$, where $!_{n}\B x\in \Lawv^{\C M_{\leq n}(X)}$ is given by 
$(!_{n}\B x)_{[a_{1},\dots, a_{k}]}=\sum_{i=1}^{k}\B x_{a_{i}}$, 
it suffices to check that $\| (!_{n}\B x)-(!_{n}\B y)\|_{\infty}\leq n\cdot \| \B x-\B y\|_{\infty}$ and apply Proposition \ref{prop:troplinear}.
\end{proof}
This result is perfectly analogous to what happens in standard models for sensitivity analysis based on the re-scaling trick recalled in Section \ref{section2}.

>>>>

To study what happens in the case of tropical Laurent series, let us first consider the case of bounded exponentials $!_{\leq n}X$:
\begin{proposition}\label{prop:boundedlip}
All tropical Laurent series $f: \Lawv^{X}\to \Lawv^{Y}$ for which $\check f:{\C M_{\leq n}(X)}\times Y\to \Lawv$, are $n$-Lipschitz-continuous.
\end{proposition}
\begin{proof}[Proof sketch]
Using the fact that $f(\B x)_{b}=\inf_{\mu\in \C M_{\leq n}(X)}\{ \check f_{\mu,b}+ \mu (!_{n}\B x) \}$, where $!_{n}\B x\in \Lawv^{\C M_{\leq n}(X)}$ is given by 
$(!_{n}\B x)_{[a_{1},\dots, a_{k}]}=\sum_{i=1}^{k}\B x_{a_{i}}$, 
it suffices to check that $\| (!_{n}\B x)-(!_{n}\B y)\|_{\infty}\leq n\cdot \| \B x-\B y\|_{\infty}$ and apply Proposition \ref{prop:troplinear}.
\end{proof}
This result is perfectly analogous to what happens in standard models for sensitivity analysis based on the re-scaling trick recalled in Section \ref{section2}.
